\Large \bf Dynamic Program Dialysis with Lya

### 2020-01-12 paper/draft.tex
Add an introductory example

A library, package, or module---we use these terms interchangeably---is a development-time construct for encapsulating reusable functionality.
This functionality falls into two categories:
  it either (i) comes bundled with the language, possibly wrapping operating-system interfaces such as the file-system in a way that is system-agnostic and conforms to the language's conventions,
  or (ii) is provided by other developers sharing code others might find useful.
Fig.~\ref{mod} depicts the basic structure of a modern program, in which the \ttt{math} library provides a set of four elementary operations.

>>>>

\begin{figure}[t]
\raggedleft 
\includegraphics[width=0.45\textwidth]{./figs/lya_ex1.pdf}
\caption{
  \textbf{Example of a library import.}
  \textmd{
    The code on the left imports the \ttt{simple-math} library, which imports a \ttt{log} library and exports a simple \ttt{Math} object.
    Several names resolve to functionality provided by the programming language:
      names \ttt{import} and \ttt{export} resolve to library-local values; \ttt{print} resolves to a global value.
  }
}
\label{fig:base}
\end{figure}

A library, package, or module---we use these terms interchangeably---is a development-time construct for encapsulating reusable functionality.
This functionality falls into two categories:
  it either (i) comes bundled with the language, possibly wrapping operating-system interfaces such as the file-system in a way that is system-agnostic and conforms to the language's conventions,
  or (ii) is provided by other developers sharing code others might find useful.
Fig.~\ref{mod} depicts the basic structure of a modern program, in which the \ttt{Math} library provides a set of four elementary operations.
